Elders Moisture Summary

### 2020-03-11 home_char_act_summary.Rmd
summary updates

---
title: "Elders home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 5 March 2020"
output:
  pdf_document: default
  word_document: default
---

@@

# Summary data for home characteristics
```{r}
# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  #filter(winter_id == 1 | winter_id == 2) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Sqft" = mean(home_sqft, na.rm = TRUE), 
            "SD Sqft" = sd(home_sqft, na.rm = TRUE), 
            "Min Sqft" = min(home_sqft, na.rm = TRUE), 
            "Median Sqft" = median(home_sqft, na.rm = TRUE), 
            "Max Sqft" = max(home_sqft, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_char_clean %>%  
  filter(winter_id == 1 | winter_id == 2) %>% 
  filter(residents_total != 0) %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_sqft, -stove_model, -home_id, -home, -treatment) 
#lapply(table_list, table)

## Select specific var to assess individually/group by area
table(table_list$winter_id, table_list$area, table_list$home_type, useNA = "ifany")

table(home_char_summary$stove_age)
```

# Summary data for home activity
```{r}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_id, -home, -treatment, 
         -intervention_date:-adult_id_num, -adult_id_char, -consent_date) 
lapply(table_list, table)

## Select specific var to assess individually/group by area
#table(table_list$home_act_sweep, table_list$area, useNA = "ifany")
```

>>>>

---
title: "Elders home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output:
  pdf_document: default
  word_document: default
---

@@

# Summary data for home characteristics
```{r}
# Summarize numeric vars: home_sqft, home_year_built, home_bedrooms, home_windows,
# home_pets, home_furry, wood_cords
home_char_summary <- home_char_clean %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #group_by(area) %>% 
  summarize("N" = n(),
            "Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE), 
            "Min" = min(wood_cords, na.rm = TRUE), 
            "Median" = median(wood_cords, na.rm = TRUE), 
            "Max" = max(wood_cords, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_char_clean %>%  
  filter(winter_id == 1) %>%  
  distinct(home, .keep_all = TRUE) %>% 
  #filter(area == "WMT") %>% 
  select(area, residents_smoke, residents_smoke_inside, home_type, home_floors,
         primary_heat, secondary_heat, stove_age, stove_cert, wood_collect,
         wood_collect_method, chimney_clean, home_damp, home_mold, home_fireplace,
         home_furnace, home_woodstove)
#lapply(table_list, table)

## Select specific var to assess individually/group by area
table(table_list$area, table_list$wood_collect_method, useNA = "ifany")

table(table_list$wood_collect_method, useNA = "ifany")
```

# Summary data for home activity
```{r}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, home_act_elect, home_act_gas, home_act_oil, home_act_other,
         home_act_propane, home_act_smoking, home_act_incense, home_act_candle,
         home_act_kerosene, home_act_windows, home_act_door, home_act_sweep) 
  #lapply(table_list, table)

## Select specific var to assess individually/group by area
table(table_list$area, table_list$home_act_elect, useNA = "ifany")

table(table_list$home_furnace, useNA = "ifany")
```

### 2020-03-11 home_characteristics_activity_cleaning.Rmd
summary updates

elders_home_char_clean <- elders_home_char %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  filter(!is.na(home_winter_id)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_over55 = 0)) %>% 
  replace_with_na(replace = list(wood_cords = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0))

>>>>

elders_home_char_clean <- elders_home_char %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  filter(!is.na(home_winter_id)) %>% 
  mutate(home_sqft = if_else(home_sqft<200, 0, home_sqft)) %>% 
  mutate(home_year_built = if_else(home_year_built<100, 0, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_over55 = 0)) %>% 
  replace_with_na(replace = list(wood_cords = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0))

### 2020-03-11 indoor_temp_rh_summary.Rmd
summary updates

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")
```

>>>>

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")

temp_rh_n <- indoor_temp_rh_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>%
  filter(!is.na(temp_indoor_current)) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  count()
```

### 2020-03-11 pm_summary_dustrak.Rmd
summary updates

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 24 Feb 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- elders_pm %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t() 
kable(pm_summary, digits = 1, align = "c")

pm_by_day <- elders_pm %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area, day_of_week) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_day

>>>>

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 10 March 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t() 
kable(pm_summary, digits = 1, align = "c")

pm_by_day <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(sampling_month) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_day

### 2020-03-11 stove_grade_usage_summary.Rmd
summary updates

---
title: "Elders stove grades and usage summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 5 March 2020"
output: pdf_document 
---

@@

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1) %>%  
  select(burn_level, wood_type, wood_type_other) 
lapply(table_list, table)
```

@@

# stove grade table
stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>%
  filter(!is.na(stove_grade)) %>% 
  ungroup() %>% 
  arrange(area, home)

table(stove_grades_filtered$stove_grade, stove_grades_filtered$area)
```

>>>>

---
title: "Elders stove grades and usage summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output: pdf_document 
---

@@

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  filter(winter_id == 1) %>%  
  filter(!is.na(burn_level)) %>% 
  select(area, sampling_visit, burn_level, wood_type, wood_type_other) 
#lapply(table_list, table)

table(table_list$wood_type)
table(table_list$area, table_list$wood_type)
table(table_list$area, table_list$burn_level, table_list$sampling_visit)
```

@@

# stove grade table
stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  #left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  #mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  #filter(pm_home == "true") %>% 
  #filter(winter_id == 1) %>%
  group_by(home, winter_id) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #filter(!is.na(stove_grade)) %>% 
  ungroup() %>% 
  filter(!is.na(stove_grade)) %>% 
  arrange(area, home)

table(stove_grades_filtered$stove_grade)
table(stove_grades_filtered$stove_grade, stove_grades_filtered$area)
table(stove_grades_filtered$stove_grade, stove_grades_filtered$area, stove_grades_filtered$winter_id)
```

### 2020-03-11 wood_moisture_summary.Rmd
summary updates

---
title: "Elders Moisture Summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 5 March 2020"
output: pdf_document
---

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")
```

@@

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home, first_datetime_new) %>% 
  separate(first_datetime_new, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

moisture_filtered <- moisture_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>%
  arrange(area, home)

moisture_filtered_time <- moisture_filtered %>% 
  # fix wrong date
  mutate(moisture_date = as.character(moisture_date),
         moisture_date = if_else(home == "CH220" & moisture_date == "2014-04-10",
                                 "2017-04-10", moisture_date),
         moisture_date = ymd(moisture_date)) %>% 
  mutate(moisture_date = ymd(moisture_date),
         first_date = ymd(first_date),
         time_diff = moisture_date - first_date,
         time_diff = as.numeric(abs(time_diff))) %>% 
  group_by(home) %>% 
  mutate(time_diff_rank = if_else(time_diff == min(time_diff, na.rm = TRUE), 1, 0)) %>%
  ungroup() %>% 
  filter(time_diff_rank == 1)
```

@@

# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(time_diff, na.rm = TRUE), 
            "SD" = sd(time_diff, na.rm = TRUE),
            "min" = min(time_diff, na.rm = TRUE), 
            "med" = median(time_diff, na.rm = TRUE), 
            "max" = max(time_diff, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")

table(moisture_filtered$area, moisture_filtered$moisture_split)
```

>>>>

---
title: "Elders Moisture Summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output: pdf_document
---

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
moisture_n <- moisture_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>%
  filter(!is.na(moisture_ave)) %>% 
  distinct(home) %>% 
  summarize(n())

summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")

summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  t() 
kable(summary_moisture, digits = 1, align = "c")
```

@@

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home, sampling_visit) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, sampling_visit, pm_home, first_datetime) %>% 
  separate(first_datetime, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

moisture_filtered <- moisture_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>%
  arrange(area, home)

moisture_filtered_time <- moisture_filtered %>% 
  mutate(moisture_date = ymd(moisture_date),
         first_date = ymd(first_date),
         time_diff = moisture_date - first_date,
         time_diff = as.numeric(abs(time_diff))) %>% 
  group_by(home, sampling_visit) %>% 
  mutate(time_diff_rank = if_else(time_diff == min(time_diff, na.rm = TRUE), 1, 0)) %>%
  ungroup() %>% 
  filter(time_diff_rank == 1)
```

@@

# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  #group_by(area) %>% 
  summarize("Mean" = mean(time_diff, na.rm = TRUE), 
            "SD" = sd(time_diff, na.rm = TRUE),
            "min" = min(time_diff, na.rm = TRUE), 
            "med" = median(time_diff, na.rm = TRUE), 
            "max" = max(time_diff, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")
```
